%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{tabto}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Olzhas Shaikenov} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\moveleft.5\hoffset\centerline{53/10 Kabanbay batyr ave.} % Your address 
\moveleft.5\hoffset\centerline{Astana 010000, Kazakhstan}
\moveleft.5\hoffset\centerline{+7 (707) 181-1234}
\moveleft.5\hoffset\centerline{olzhas.shaikenov@nu.edu.kz}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

As a bachelor student with high academic performance I aim to find an internship which will help me to obtain new knowledge which can be useful for my future career. I have gained much knowledge in circuit design, simulations, electromagnetics and multi-frequency analysis, and now I got inspired by using this knowledge in practice. Also, I like to solve complicated mathematics problems which can be very useful in engineering studies.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelor degree} \hfill August 2015 - Present \\
Department of Electrical and Computer Engineering, School of Engineering, Nazarbayev University
\begin{itemize}
\item Cumulative GPA (Grade Point Average): 3.32/4.0.
\end{itemize} 

{\sl High school} \hfill August 2012 - June 2015 \\
Regional Multidisciplinary Lyceum for gifted children
\begin{itemize}
\item Altyn Belgy (excellent student in Kazakhstani high school).
\item Excellent student of UNT (United National Test): 120/125/
\item "The best graduate student" award winner/
\end{itemize} 

%----------------------------------------------------------------------------------------
%	RESEARCH INTEREST SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH \\ INTEREST}
RF circuits design, Electromagnetics, Multi-Frequency or Broadband RF Power Amplifier Architecture, Signal Processing in RF circuits, Epidemic Modelling.

\iffalse
%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH \\ EXPERIENCE}


{\sl Research Assistant} \hfill February 2018 - Present \\
Dr. Aresh Haresh Dadlani's research group, Nazarbayev University
\begin{itemize}
\item Working on Epidemic modelling research
\item Working on Wireless Sensors Networks
\item Learning how to simulate different epidemic models in MATLAB language
\item Collaborating with Kansas State University research group concerning their research about epidemic modelling
\end{itemize} 
Results: 
\begin{itemize}
\item Sufficient MATLAB programming experience
\item Useful experience in group working with other researchers
\item Draft of the paper about smart grid revenue maximization for submission to IEEE conferences
\end{itemize} 
 \fi
 
 \iffalse
 %----------------------------------------------------------------------------------------
%	PROJECTS AT NU SECTION
%----------------------------------------------------------------------------------------
 
\section{PROJECTS}
  
{\sl Microelectronic Devices and Circuits} \hfill Fall 2017 \\
Used tools: LTspice
\begin{itemize}
\item Design of a circuit which gives transfer characteristics similar to TANH function 
\end{itemize} 

{\sl Computer Systems Architecture} \hfill Spring 2018 \\
Used tools: Java
\begin{itemize}
\item Assembly level programming: a program that converts assembly level code to machine language hex code
\end{itemize} 

{\sl Software Engineering} \hfill Spring 2018 \\
Used tools: Java
\begin{itemize}
\item Library Management System: design of a Java Swing app for library with different features
\end{itemize} 

{\sl Digital Electronic System Design} \hfill Spring 2018 \\
Used tools: VHDL
\begin{itemize}
\item Seatbelt program which makes a sound when it is not connected
\end{itemize} 

{\sl Digital Integrated Circuits Design} \hfill Fall 2018 \\
Used tools: Electric VLSI
\begin{itemize}
\item Book chapter on different types of basic logic gates, performance comparing, selecting the best one in terms of area, power consumption, etc.
\end{itemize} 

 \fi 
 %----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{WORK \\ EXPERIENCE}

{\sl Software Engineer Intern} \hfill May 2018 - August 2018 \\
Engineering Center of the Department of Material and Technical Supply LLP, Astana, Kazakhstan
\begin{itemize}
\item Working on Visual Studio web application.
\item Creating front end HTML site layout with some CSS design.
\end{itemize} 

{\sl Dispatcher Assistant} \hfill May 2016 - July 2016 \\
Unistroy-PV LLP, Pavlodar, Kazakhstan
\begin{itemize}
\item Preparing the plan of daily transportation for trucks.
\item Control of trucks documents and fuel consumption.
\end{itemize} 



%----------------------------------------------------------------------------------------
%	 SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{SKILLS} 

\begin{itemize}
\item Was enrolled in Dr. Aresh Haresh Dadlani's (Assistant Professor in Nazarbayev University) research about epidemic modelling, wireless sensors networks and smart grid revenue maximization. Collaborated with Kansas State University research group concerning their research about epidemic modelling. Wrote a draft of the paper about a smart grid revenue maximization for submission to IEEE conferences.
\item C language\\
Completed project on LDA, RLDA, SEDC classifiers analysis.
\item Embedded C\\
Wrote codes for 8051 microcontrollers and implemented them on the board.
\item Java\\
Completed an assembly to machine language converter and a library management system with a large database and Java Swing interface.
\item MATLAB\\
Implemented epidemic spreading processes simulations of large scale networks and a revenue maximization technique implementation.
\item LTspice\\
Completed several projects with theoretical circuit simulations, such as implementing a circuit with IV characteristics similar to hyperbolic tangent function. 
\item Electric VLSI\\ 
Completed a team project “Physical design of gates” where schematics and layouts of different gates were implemented and analyzed in terms of cost, efficiency, speed. This project also describes VLSI and its checking tools (DRC, ERC and NCC) and the use of stick diagrams.
\item Worked in ADS, CST, HFSS, Mathematica, LATEX, PSIM, VHDL with transfer to FPGA.


\end{itemize}
 
%----------------------------------------------------------------------------------------
%	HONORS SECTION
%---------------------------------------------------------------------------------------- 

\section{HONORS \\ AWARDS}
\begin{itemize}
\item 1st place Regional Junior Mathematics Olympiad \hfill 2011 
\item 1st place Regional Mathematics Olympiad  \hfill 2014 
\item Participant of Republic Mathematics Olympiad \hfill 2014 
\item 3rd place Regional Mathematics Olympiad \hfill 2013, 2015 



\end{itemize}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Nazarbayev University Volunteers Club, {\sl Member} \hfill September 2015 - Present\\
Nazarbayev University IEEE Student Chapter, {\sl Member} \hfill September 2017 - Present \\
 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}